Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-10-10 main.tex
Ensure a max of 6 authors are listed.

\bibitem{Knight2016}
Knight V, Campbell O, Harper M, Langner K, Campbell J,
  Campbell T, Carney A, Chorley M, Davidson-pilon C,
  Glynatsi N, Ehrlich T, Jones M, Koutsovoulos G, Muller J, Palmer G, Petunov P, Slavin P,
  Standen T, Visintini L, and Molden K.
\newblock {An Open Framework for the Reproducible Study of the Iterated
  Prisoner ' s Dilemma}.
\newblock 2016.

@@

\bibitem{Nowak2017}
Allen B, Lippner G, Chen Y, Fotouhi B, Momeni N,
  Shing-Tung Yau, and Martin~A Nowak.
\newblock {Evolutionary dynamics on any population structure}.
\newblock 544:227--230, March 2017.

@@

\bibitem{Wilson2014}
Wilson G , Aruliah D, Brown T, Chue~Hong N, Davis M ,
  Guy R , Haddock S , Huff K, Mitchell I , Plumbley M , 
  Waugh B , White E , and Wilson P.
\newblock {Best Practices for Scientific Computing}.
\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.

>>>>

\bibitem{Knight2016}
Knight V, Campbell O, Harper M, Langner K, Campbell J,
  Campbell T, et al.
  \newblock {An Open Framework for the Reproducible Study of the Iterated
  Prisoner ' s Dilemma}.
\newblock 2016.

@@

\bibitem{Nowak2017}
Allen B, Lippner G, Chen Y, Fotouhi B, Momeni N,
  Shing-Tung Yau et al.
\newblock {Evolutionary dynamics on any population structure}.
\newblock 544:227--230, March 2017.

@@

\bibitem{Wilson2014}
Wilson G , Aruliah D, Brown T, Chue~Hong N, Davis M ,
  Guy R , et al.
  \newblock {Best Practices for Scientific Computing}.
\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
